Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute rate.fail and rate.low together with rate.take

# Probability of taking a course
d_support$TNT <- d_transcript_augmented %>%

@@

  mutate(rate.take = n_distinct(`Student ID`) / n_students)
```

@@

```{r}
#
# Probability of failing, having a low grade
d_support$PF_HL <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low")
    )

>>>>

# Probability of taking / failing / obtaining of low grade a course
d_support$TPH <- d_transcript_augmented %>%

@@

  mutate(
    rate.take = n_distinct(`Student ID`) / n_students,
    rate.fail = mean(Grade < pass_grade),
    rate.low  = mean(Grade < high_grade)
    )
```

@@

```{r}
#
# Probability of failing, having a low grade
